%-----------------------------------------------------
% Simon M. Mudd CV
%
% This CV is loosely based on the template produced by
% Dario Taraborelli
% URL: http://nitens.org/taraborelli/cvtex
%
% NOTE: This gives a load of error messages but in the end produces 
% a pdf of the cv, so I just ignore all the errors. 
%
%----------------------------------------------------

%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

\documentclass[10pt, a4paper]{article}
\usepackage{fontspec} 
\usepackage{eurosym}
% DOCUMENT LAYOUT
\usepackage{geometry} 
\geometry{a4paper, textwidth=5.75in, textheight=9.5in, marginparsep=7pt, marginparwidth=.6in}
\setlength\parindent{0in}

% FONTS
\usepackage{xunicode}
\usepackage{xltxtra}
\defaultfontfeatures{Mapping=tex-text} % converts LaTeX specials (``quotes'' --- dashes etc.) to unicode
%For gentium, you should install the font from here: http://scripts.sil.org/cms/scripts/page.php?site_id=nrsi&item_id=Gentium_basic
%\setromanfont [Ligatures={Common}, BoldFont={Gentium Basic Bold}, ItalicFont={Gentium Basic Italic}]{Gentium Basic}

%For fontin font, you should install the font from here: http://www.exljbris.com/fontin.html
%\setromanfont [Ligatures={Common}, BoldFont={Fontin Bold}, ItalicFont={Fontin Italic}]{Fontin}

%For linux libertine font, you should install from fontsquirrel, http://www.fontsquirrel.com/
% This one seems to be happiest! Least bad boxes. And looks nice
%\setromanfont [Ligatures={Common}, BoldFont={Linux Libertine Bold}, ItalicFont={Linux Libertine Italic}]{Linux Libertine}

%For Liberation Serif font, you should install from fontsquirrel, http://www.fontsquirrel.com/
%\setromanfont [Ligatures={Common}, BoldFont={Liberation Serif Bold}, ItalicFont={Liberation Serif Italic}]{Liberation Serif}

%For Heuristica Serif font, you should install from fontsquirrel, http://www.fontsquirrel.com/
% This one also seems to make XeLaTeX happy
\setromanfont [Ligatures={Common}, BoldFont={Liberation Serif Bold}, ItalicFont={Liberation Serif Italic}]{Liberation Serif}

%\setmonofont[Scale=0.8]{Monaco}

%You can download fontawsome here: http://fontawesome.io/
% once you unzip it you will need to go into the folder and install the fonts
\usepackage{fontawesome}

% ---- CUSTOM COMMANDS
\chardef\&="E050
\newcommand{\html}[1]{\href{#1}{\scriptsize\textsc{[html]}}}
\newcommand{\pdf}[1]{\href{#1}{\scriptsize\textsc{[pdf]}}}
\newcommand{\doi}[1]{\href{#1}{\scriptsize\textsc{[doi]}}}


% ---- MARGIN YEARS
\usepackage{marginnote}
\newcommand{\amper{}}{\chardef\amper="E0BD }
\newcommand{\years}[1]{\marginnote{\scriptsize #1}}
\renewcommand*{\raggedleftmarginnote}{}
\setlength{\marginparsep}{7pt}
\reversemarginpar

% HEADINGS
\usepackage{sectsty} 
\usepackage[normalem]{ulem} 
\sectionfont{\mdseries\upshape\Large}
\subsectionfont{\mdseries\scshape\normalsize} 
\subsubsectionfont{\mdseries\upshape\large} 

%columns
\usepackage{multicol}
\setlength{\columnsep}{10pt}
%\def\columnseprulecolor{\color{White}}

% PDF SETUP
% ---- FILL IN HERE THE DOC TITLE AND AUTHOR
\usepackage[bookmarks, colorlinks, breaklinks, 
% ---- FILL IN HERE THE TITLE AND AUTHOR
	pdftitle={Boris Gailleton - vita},
	pdfauthor={Boris Gailleton},
]{hyperref}  
\hypersetup{linkcolor=blue,citecolor=blue,filecolor=black,urlcolor=blue} 

%Colours
\usepackage[usenames,dvipsnames]{xcolor}
\definecolor{Gray}{rgb}{0.3,0.3,0.3}
\definecolor{LightGray}{rgb}{0.6,0.6,0.6}

% Header and footer
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\rhead{\textcolor{LightGray}{Boris Gailleton CV, July, 2019}}
\renewcommand{\footrulewidth}{1pt}
\rfoot{\textcolor{LightGray}{Page \thepage}}

%urls
\usepackage{url}

% DOCUMENT
\begin{document}
{\LARGE Boris Gailleton}\\
\textcolor{Gray}{\large{Early Stage Researcher in Earth Surface Processes}}\\[0.2cm]

\begin{multicols}{2}
University of Edinburgh\\
School of GeoSciences\\
Drummond Street\\
Edinburgh, EH8 9XP\\
United Kingdom

\columnbreak

Phone: \texttt{+44~(0)756~395~3339}\\
% Fax: \texttt{+44~(0)131~650~2524}\\
email: \href{mailto:b.gailleton@sms.ed.ac.uk}{b.gailleton@sms.ed.ac.uk}\\
Google Scholar: \href{https://scholar.google.co.uk/citations?user=r5HIc00AAAAJ&hl=en}{Boris Gailleton}\\ 
Github: \href{https://github.com/bgailleton}{bgailleton}\\
ORCID: \href{https://orcid.org/0000-0001-6518-4304}{ORCID 0000-0001-6518-4304}\\

\end{multicols}

\hrule
\section*{Appointments}
\noindent
\years{2016 - now}\textbf{Early Stage Researcher} in \textit{Atmospheric and Environmental Sciences: School of GeoSciences}, University of Edinburgh, UK\\[0.05cm]
\years{2019}\textbf{Research Software Engineer} in \textit{Landslide Dynamics} (3 months): School of GeoSciences, University of Edinburgh, UK\\[0.05cm]
\years{2015}\textbf{Research Engineer} in \textit{Ore deposit characterisation}: ArcelorMittal Research Mining Centre, Maizière-lès-Metz, France \\[0.05cm]


\hrule
\section*{Education}
\noindent
\years{2016 - now}\textbf{PhD} in \textit{Atmospheric and Environmental Sciences}, School of GeoSciences, University of Edinburgh, UK\\[0.05cm]
\years{2015}\textbf{MA} in \textit{Mining Geology}, UniLaSalle, Beauvais, France - Laurentian University, Sudbury, ON, Canada\\[0.05cm]
\years{2013}\textbf{BA} in \textit{Geology}, UniLaSalle (former LaSalle Beauvais), Beauvais, France\\[0.05cm]

\hrule
\section*{Awards}
\noindent
\years{2017}\textbf{Best Poster Award}, Geosciences Gradschool Conference, University of Edinburgh\\[0.05cm]
\years{2015}\textbf{Graduation with Honors}, Awarded by the graduation committee of UniLaSalle\\[0.05cm]

\hrule
\section*{Funding}
\noindent
\years{2016 - 2020}European Union initial training grant 674899 - Horizon 2020 -  (\href{http://www.subitop.eu}{SUBITOP})\\ Funding Agency: \textit{ERC}\\Award: \textbf{54,000}\euro \textit{(research budget)} \\[0.05cm] P.I. Niels Holvius, Hugh D. Sinclair, Simon M. Mudd\\[0.05cm]

\hrule
\section*{Service}
\years{2019}\textbf{Conference Co-Organiser}, (\href{http://topoeurope2019.eu/}{TopoEurope conference}, part of SUBITOP ITN)\\[0.05cm]
\years{2019}\textbf{Co-Convener}, EGU general assembly: GM12.2/HS12.11/NH10.7/SSS13.39 Making high resolution topographic analysis more reproducible with LSDTopoTools\\[0.05cm]
\years{2018}\textbf{Journal Peer Reviewer}: Journal of Geophysical Research: Earth Surface; Geomorphology\\[0.05cm]
\years{2016 - 2017}\textbf{Hutton Club Seminar Series Convener}: University of Edinburgh\\[0.05cm]

\hrule
\section*{Invited Talks}
\years{2018}\textbf{Freie Universit\"at Seminar Series, Berlin, Germany}, Invited talk to the Sedimentary System Research Group\\[0.05cm]

\hrule
\section*{Demonstrating/Tutoring activities}
\years{2018}Eroding Landscapes - Field demonstrator (2 days) (4th year Undergraduates)\\[0.05cm]
\years{2018}Technological Infrastructures for GIS (Master course) - Demonstrator\\[0.05cm]
\years{2017--2018}Geomorphology (2nd year Undergraduates), Tutoring (24 Hours), with Anthony Newton.
\years{2017}Global Tectonics and the Rock Cycle (Field trip) (1st year Undergraduates) - Demonstrating (2 days) \\[0.05cm]
\years{2017}Global Tectonics and the Rock Cycle (1st year Undergraduates) - Demonstrating (24 hours) \\[0.05cm]
\years{2015}Paleontology (1st year Undergraduates) - Demonstrating (8 hours) \\[0.05cm]
\years{2014}Phase Diagram in magmas - Igneous Petrology (3rd year Undergraduates), Demonstrating (12 hours)\\[0.05cm]
\years{2014}Field Igneous Geology - Field Demonstrator - 2 weeks, La Bourboule area, Massif Central, France (2nd year Undergraduates) \\[0.05cm]

\hrule
\section*{Software}
Most of my software contributions to research have been published and released within \href{https://lsdtopotools.github.io/}{LSDTopoTools Research software} and to lesser extent on my \href{https://github.com/bgailleton}{Personal Github}.
\subsection*{Published}

\years{Github}The LSDTopoTools software package for topographic analysis has a number of repositories located on the \href{https://github.com/LSDtopotools}{Github LSDTopoTools page}, Lead Developer: Simon M. Mudd\par

\years{Zenodo}The LSDTopotools development team has released a number of packages via Zenodo within the \href{https://zenodo.org/search?page=1&size=20&q=lsdtopotools}{LSDTopoTools software package,}\par

Mudd, S. M., Clubb, F. J., Grieve, S. W. D., Milodowski, D. T., Hurst, M. D., Gailleton, B., and Valters, D. A. (2019, June 13). LSDTopoTools2 (Version v0.02). Zenodo.\\ \href{http://doi.org/10.5281/zenodo.3245041}{http://doi.org/10.5281/zenodo.3245041} \textit{Contribution: General contributions to the tools, DEM preprocessing algorithm, knickpoint detection algorithm, chi tools, drainage divide characterisation algorithms, testing.}\par

Mudd, S. M., Clubb, F. J., Gailleton, B., Grieve, S. W. D., Valters, D. A., and Hurst, M. D. (2019, February 8). LSDTopoTools Documentation (Version v2.0). \textit{Zenodo}.\\ \href{http://doi.org/10.5281/zenodo.2560224}{http://doi.org/10.5281/zenodo.2560224} \textit{Contribution: Knickpoint algorithm documentation, some sections about the chi tools.}\par

Mudd, S. M., Clubb, F. J., Gailleton, B., Valters, D. A., Hurst, M. D., and Grieve, S. W. D. (2019, February 8). LSDMappingTools (Version v0.1). \textit{Zenodo}.\\ \href{http://doi.org/10.5281/zenodo.2560166}{http://doi.org/10.5281/zenodo.2560166} \textit{Contribution: General contributions to the plotting and I/O routines.}\par 

Mudd, S. M., Clubb, F. J., Gailleton, B., Hurst, M. D., Milodowski, D. T., and Valters, D. A. (2018, June 18). The LSDTopoTools Chi Mapping Package (Version 1.11). \textit{Zenodo}.\\ \href{http://doi.org/10.5281/zenodo.1291889}{http://doi.org/10.5281/zenodo.1291889} \textit{Contribution: General contributions to the chi tools.}\par

\subsection*{In preparation}

\years{In preparation} I am developing two main packages focused on topographic analysis and Landscape Evolution Models, both designed to combine the flexibility and approachability of python with the computational efficiency  of C++. They can be accessed on demand before their release with associated publications.\par

Gailleton, B., Mudd, S. M., , Graf E.L.S. (in prep.). Carpythians, a lightweight python - C++ Landscape Evolution Model.\par

Gailleton, B., Mudd, S. M., Clubb, F. J., Valters, D. A., Hurst, M. D., Grieve, S. W. D., Milodowski, D. T. and , Graf E.L.S. (in prep.). lsdtopytools, a python wrapper, high-level interface and automator for LSDTopoTools.\par


\hrule
\section*{Publications}

\subsection*{Published}

\years{2019}\hangindent=0.7cm Gailleton, B., Mudd, S. M., Clubb, F. J., Peifer, D. and Hurst, M. D.: A segmentation approach for the reproducible extraction and quantification of knickpoints from river long profiles, Earth Surface Dynamics, 7(1), 211-230, doi:10.5194/esurf-7-211-2019, 2019.\par
\years{2019}\hangindent=0.7cm Bernard, T., Sinclair, H. D., Gailleton, B., Mudd, S. M. and Ford, M.: Lithological control on the post-orogenic topography and erosion history of the Pyrenees, Earth and Planetary Science Letters, 518, 53-66, doi:10.1016/j.epsl.2019.04.034, 2019. \textit{Contribution: Ran and analysed sensitivity analysis on the relationship between $k_{sn}$, concavity and lithology; processed and analysed swath profiles to quantify the relationship between elevation and lithology.}\par
\years{2018}\hangindent=0.7cm Mudd, S. M., Clubb, F. J., Gailleton, B. and Hurst, M. D.: How concave are river channels?, Earth Surface Dynamics, 6(2), 505-523, doi:10.5194/esurf-6-505-2018, 2018. \textit{Contribution: Ran analysis on some test sites and debugged the software. Focused on the relationship between lithology and river concavity.}\par

%\noindentEARTH AND PLANETARY SCIENCE LETTERS

\subsection*{In preparation}
\years{2020?}\hangindent=0.7cm Sinclair H.D., Gailleton B., Walcott, R.C, Naylor, M., Mudd, S.M.: Drainage capture expands big Himalayan rivers, 2020. \textit{Contribution: Topographic analysis on rivers and drainage divide across the Nepalese Himalayas.}\par
\years{2020?}\hangindent=0.7cm Gailleton B., Sinclair H.D., Mudd, S. M., Matenco L., Graf E.L.S.: Tectonics from topography in lithologically ambiguous landscapes, 2020.\par


\raggedright
% In review papers. These can be commented out if you want to hide them
%\years{in review}\hangindent=0.7cm\textbf{39.}


% \subsection*{Other Contributions}
% \noindent
% \years{2014}\hangindent=0.7cm\textbf{4.} Mudd, S. M., K. Yoo, and B. Weinman (2014), Quantifying geomorphic controls on time in weathering systems, edited by J. Gaillardet, \textit{Geochemistry of the Earth's Surface GES-10}, 10, 249-253, \href{http://dx.doi.org/doi:10.1016/j.proeps.2014.08.033}{doi:10.1016/j.proeps.2014.08.033}.\par
% \hangindent=0.7cm\textbf{3.} Mudd, S. M. (2014), Slope Processes, \textbf{Oxford Bibliographies}, \href{http://dx.doi.org/doi:10.1093/OBO/9780199874002-0083}{doi:10.1093/OBO/9780199874002-0083}.\par 
% \years{2011}\hangindent=0.7cm\textbf{2.} Mudd, S. M. (2011), The life and death of salt marshes in response to anthropogenic disturbance of sediment supply, \textit{Geology}, 39(5), 511-512, \href{http://dx.doi.org/doi:10.1130/focus052011.1}{doi:10.1130/focus052011.1}.\par
% \years{2009}\hangindent=0.7cm\textbf{1.} Yoo, K., B. Weinman, S. M. Mudd, M. Hurst, M. Attal, and K. Maher (2011), Evolution of hillslope soils: The geomorphic theater and the geochemical play, \textit{Applied Geochemistry}, 26, S149-S153, \href{http://dx.doi.org/doi:10.1016/j.apgeochem.2011.03.054}{doi:10.1016/j.apgeochem.2011.03.054}.\par

%\vspace{1cm}
\vfill{}
%\hrulefill


\end{document}